---
title: "Building blocks of a clinical outcome report"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Building blocks of a clinical outcome report}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", fig.width = 7, fig.height = 4)
```

PhysioReport assembles parameterized, bilingual, colorblind-safe clinical
reports (gait, HRV, EMG) with normative overlays and change annotated against
measurement-error thresholds. This vignette walks the reusable building blocks
that a full report is made of. Everything here runs offline on the package's
hard dependencies (`PhysioExperiment` and `ggplot2`).

```{r setup}
library(PhysioReport)
```

## Normative reference and z-scores

A `NormativeModel` describes the expected mean/SD of a measurement -- as a
scalar, a per-timepoint waveform corridor, a stratified table, or a lookup
function. `normativeZScore()` standardizes an observation against it.

```{r norm}
speed_norm <- NormativeModel(mean = 1.30, sd = 0.15, source = "Bohannon 1997")
speed_norm
normativeZScore(c(0.90, 1.30, 1.55), speed_norm)
```

`plotNormativeBand()` draws the graded +/-1 SD and +/-2 SD corridor and overlays
an observed trajectory -- here a knee-flexion gait-cycle waveform:

```{r band}
knee_norm <- NormativeModel(
  mean = sin(seq(0, pi, length.out = 101)),
  sd   = rep(0.1, 101),
  time = 0:100,
  source = "Reference gait corridor"
)
set.seed(1)
observed <- sin(seq(0, pi, length.out = 101)) + rnorm(101, 0, 0.05)
plotNormativeBand(observed, knee_norm)
```

## Change against MDC and MCID

`annotateChange()` classifies each pre-to-post change as *no change*,
*detectable* (clears the Minimal Detectable Change), or *clinically meaningful*
(clears the Minimal Clinically Important Difference), tracking benefit direction
so that decrease-is-good metrics (pain, timed tests) are handled correctly.

```{r change}
chg <- annotateChange(
  pre       = c(fma = 20, pain = 7),
  post      = c(fma = 31, pain = 4),
  mdc       = c(5.2, 1.0),
  mcid      = c(9, 2),
  direction = c("increase", "decrease")
)
chg[, c("metric", "change", "classification")]
```

## Single-case designs

For n-of-1 / single-case experimental designs, `plotSCED()` draws the
SCED-standard overlays (phase shading, per-phase means, the baseline +/-2 SD
band, and split-middle celeration lines):

```{r sced}
plotSCED(c(2, 3, 2, 3, 6, 7, 8, 7), rep(c("A", "B"), each = 4))
```

(The effect-size summary `scedStats()` delegates to the peer-reviewed estimators
in the optional `PhysioClinStats` package.)

## Bilingual labels

Every axis label and caption flows through `physioLabel()`, so the same report
renders in English or Japanese:

```{r i18n}
c(en = physioLabel("session", "en"), ja = physioLabel("session", "ja"))
```

## Where to go next

* `?NormativeModel` / `?plotNormativeBand` -- normative corridors.
* `?annotateChange` / `?plotChangeAnnotated` -- MDC/MCID change.
* `?clinicalGaitReport` / `?renderClinicalReport` -- the full parameterized
  gait/HRV/EMG reports (some need optional ecosystem packages, e.g.
  `PhysioMoCap`, `officer`).
